Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-04 paper/main.tex
Updates

Using this mixed data partial association measure, we propose a method to rank
CI tests, and use it for model construction and modification. Given a
potentially empty DAG $ G $ and a dataset $ D $, for each pair for variable $ X
$ and $ Y $ in $ G $:
\begin{itemize}
	\item If there is no edge between $ X $ and $ Y $, we compute p-value for the CI test $ X \ci Y \rvert pa_G(X) \cup pa_G(Y) $ and the partial association measure: $ \rho(X, Y; pa_G(X) \cup pa_G(Y)) $.
	\item If there is an edge between $ X $ and $ Y $, we compute p-value for the CI test $ X \ci Y \rvert pa_{\underline{G}}(X) \cup pa_{\underline{G}}(Y) $ and the partial association measure: $ \rho(X, Y; pa_{\underline{G}}(X) \cup pa_{\underline{G}}(Y) $.
\end{itemize}

>>>>

Using this mixed data partial association measure, we now propose a method for
construcing DAGs while incorporating expert knowledge iteratively. Given a
potentially empty DAG $ G $ and a dataset $ D $, a p-value threshold of $
\alpha $ and a measure of association threshold of $ \beta $, the construction
procedure works as follows:

\begin{enumerate}
	\item For each pair of variables $ X $ and $ Y $ in the model:
		\begin{itemize}
			\item If there is an edge between $ X $ and $ Y $, remove the edge to obtain the DAG $ \underline{G} $, and 
				compute the measure of association $ \phi(X, Y \rvert \underline{G}_{pa}(X) \cup \underline{G}_{pa}(Y)) $
			\item If there is no edge between $ X $ and $ Y $, compute the measure of association $ \phi(X, Y \rvert G_{pa}(X) \cup \underline{G}_{pa}(Y) $.
		\end{itemize}
	\item If for any pair $ X $ and $ Y $, if there is an edge between them with p-value $ > \alpha $ and $ \phi < \beta $, remove the edge between them.
	\item For the remaining $ X $ and $ Y $ pairs with p-value $ \geq \alpha $, sort them by $ \beta $. Select the pair with highest $ \beta $, ask the user to specify the direction between $ X $ and $ Y $ and add the edge to $ G $.
\end{enumerate}
